Modal Abstractions for Virtualizing Memory Addresses

### 2024-07-24 examples.tex
walkpgdir
+

 $\specline{\textsf{P} \ast \textsf{entry} \mapsto_{\textsf{id}} \textsf{\_} \ast \mathcal{I}\texttt{ASpace}_{\textsf{id}}(\theta,\Xi,m) \ast \ghostmaptoken{\delta{}s}{\rtv}{\delta}}_{\rtv}$

@@

$\specline{\textsf{P} \ast \mathcal{I}\texttt{ASpace}_{\textsf{id}}(\theta,\Xi\setminus\{\textsf{entry}\},m)  }_{\rtv}$

@@

$\specline{\textsf{P} \ast \mathcal{I}\texttt{ASpace}_{\textsf{id}}(\theta,\Xi\setminus\{\textsf{entry},\textsf{entry}_{\textsf{pfn}}\},m)  }_{\rtv}$
$\specline{ \textsf{entry+KERNBASE} \mapsto_{\textsf{vpte,qfrac}} \textsf{entry\_val} \ast \ulcorner  \textsf{qfrac} = 1 \leftrightarrow \; \lnot(\textsf{entry\_present entry\_val})\urcorner}_{\rtv}$
$\specline{ \textsf{entry}_{\textsf{pfn}} \mapsto_{\textsf{v,qf}} \textsf{pdp\_val} \ast \textsf{rax} \mapsto_{\textsf{r}} \textsf{entry}_{\textsf{pfn}}}_{\rtv}$    

@@

@@

@@

$\specline{\textsf{P} \ast \mathcal{I}\texttt{ASpace}(\theta,m)  \ast \texttt{rdi}\mapsto_{r} \textsf{plm4} \ast \texttt{rsi}\mapsto_{r} \textsf{va} \ast  \texttt{rdx}\mapsto_{r} \textsf{pa} \ast \texttt{rcx}\mapsto_{r} \textsf{perm} \ast \texttt{rax}\mapsto_{\textsf{r}} \textsf{pte\_addr} \ast }_{\rtv}$
$\specline{\ulcorner \texttt{aligned va} \land  \theta \; !!\; \vaddr = \texttt{None}\urcorner\ast \textsf{vl4} \mapsto_{\textsf{vpte,qfrac}} \textsf{l4e l4} \ast \textsf{vl3} \mapsto_{\textsf{vpte,qfrac}} \textsf{l3e l3} \ast \textsf{vl2} \mapsto_{\textsf{vpte,qfrac}} \textsf{l2e pa}  \ast }_{\rtv}$
$\specline{\textsf{pte\_addr} \mapsto_{\textsf{vpte,qfrac}} \textsf{pa} \textsf{pte\_val} \ast \ulcorner  \textsf{qfrac} = 1 \leftrightarrow \lnot (\textsf{entry\_present pte\_val}) \urcorner}_{\rtv}$     
$\specline{\texttt{rbp-8}\mapsto_{v} \textsf{plm4} \ast \texttt{rbp-16}\mapsto_{v} \textsf{va}  \ast \texttt{rbp-24}\mapsto_{v} \textsf{pa} \ast \texttt{rbp-32}\mapsto_{v} \textsf{perm} \ast \textsf{r8} \mapsto_{\textsf{r}} \textsf{\_}}_{\rtv}$      

@@

$\specline{\textsf{P} \ast \mathcal{I}\texttt{ASpace}(\theta,m)  \ast \texttt{rdi}\mapsto_{r} \textsf{plm4} \ast \texttt{rsi}\mapsto_{r} \textsf{va} \ast  \texttt{rdx}\mapsto_{r} \textsf{pa} \ast \texttt{rcx}\mapsto_{r} \textsf{perm} \ast \texttt{rax}\mapsto_{\textsf{r}} \textsf{pte\_addr} \ast \ulcorner \texttt{aligned va} \land  \theta \; !!\; \vaddr = \texttt{None}\urcorner\ast }_{\rtv}$
$\specline{\textsf{pte\_addr} \mapsto_{\textsf{vpte,qfrac}} \textsf{pa} \textsf{pte\_val} \ast \ulcorner \lnot \textsf{qfrac} = 1 \land \lnot(\textsf{entry\_present pte\_val}) \urcorner}$     
$\specline{\texttt{rbp-8}\mapsto_{v} \textsf{plm4} \ast \texttt{rbp-16}\mapsto_{v} \textsf{va}  \ast \texttt{rbp-24}\mapsto_{v} \textsf{pa} \ast \texttt{rbp-32}\mapsto_{v} \textsf{perm} \ast \textsf{r8} \mapsto_{\textsf{r}} \textsf{\_}}_{\rtv}$      

@@

$\specline{\textsf{P} \ast \mathcal{I}\texttt{ASpace}(\theta,m)  \ast \texttt{rdi}\mapsto_{r} \textsf{plm4} \ast \texttt{rsi}\mapsto_{r} \textsf{va} \ast  \texttt{rdx}\mapsto_{r} \textsf{pa} \ast \texttt{rcx}\mapsto_{r} \textsf{perm} \ast \texttt{rax}\mapsto_{\textsf{r}} \textsf{pte\_addr} \ast \ulcorner \texttt{aligned va} \land  \theta \; !!\; \vaddr = \texttt{None}\urcorner\ast }_{\rtv}$
$\specline{\textsf{pte\_addr} \mapsto_{\textsf{vpte,qfrac}} \textsf{pa} (\textsf{pa}>>12) \ast \ulcorner \lnot \textsf{qfrac} = 1 \land \lnot(\textsf{entry\_present pte\_val}) \urcorner}$     
$\specline{\texttt{rbp-8}\mapsto_{v} \textsf{plm4} \ast \texttt{rbp-16}\mapsto_{v} \textsf{va}  \ast \texttt{rbp-24}\mapsto_{v} \textsf{pa} \ast \texttt{rbp-32}\mapsto_{v} \textsf{perm} \ast \textsf{r8} \mapsto_{\textsf{r}} \textsf{\_}}_{\rtv}$      

@@

  \caption{Specification and proof of code for mapping a new page.}

>>>>

 $\specline{\textsf{P} \ast \textsf{plm4} \mapsto_{\textsf{id}} \textsf{\_} \ast \mathcal{I}\texttt{ASpace}_{\textsf{id}}(\theta,\Xi,m) \ast \ghostmaptoken{\delta{}s}{\rtv}{\delta}}_{\rtv}$

@@

$\specline{\textsf{P} \ast \mathcal{I}\texttt{ASpace}_{\textsf{id}}(\theta,\Xi\setminus\{\textsf{plm4\_entry}\},m)  }_{\rtv}$
$\specline{ \ghostmaptoken{\textsf{id}}{(\mathsf{plm4\_entry})}{\textsf{4}} \ast \ghostmaptoken{\delta{}s}{\rtv}{\delta}  }_{\rtv}$
$\specline{\begin{array}{l} \textsf{entry\_present(l4e\_val)} -* \\  \;\;\;\;\;\;\; \forall_{i\in\textsf{0..511}} \; \textsf{table\_root(plm4)}_{pfn} \textsf{ + i * 8} \mapsto_{\textsf{id}} \textsf{3}    \end{array}}_{\rtv} $
$\specline{ \textsf{plm4\_entry+KERNBASE} \mapsto_{\textsf{vpte,qfrac}} \textsf{plm4 l4e\_val} \ast \ulcorner  \textsf{qfrac} = 1 \leftrightarrow \; \lnot(\textsf{entry\_present l4e\_val})\urcorner}_{\rtv}$    

@@

$\specline{\textsf{P} \ast \mathcal{I}\texttt{ASpace}_{\textsf{id}}(\theta,\Xi\setminus\{\textsf{plm4\_entry}\},m)  }_{\rtv}$
$\specline{ \ghostmaptoken{\textsf{id}}{(\mathsf{plm4\_entry})}{\textsf{4}}  \ast \ghostmaptoken{\delta{}s}{\rtv}{\delta}  }_{\rtv}$
$\specline{\forall_{i\in\textsf{0..511}} \; \textsf{table\_root(plm4\_entry}_{\textsf{pfn}}) \textsf{ + i * 8} \mapsto_{\textsf{id}} \textsf{3} } $
$\specline{ \textsf{plm4\_entry+KERNBASE} \mapsto_{\textsf{vpte,qfrac}} \textsf{plm4\_entry l4e\_val} \ast \ulcorner  \textsf{qfrac} = 1 \leftrightarrow \; \lnot(\textsf{entry\_present l4e\_val})\urcorner}_{\rtv}$
$\specline{\texttt{rax}  \mapsto_{\textsf{r}} \textsf{table\_root(pml4\_entry}_{\textsf{pfn}})}_{\rtv}$

@@

$\specline{\textsf{pdp}+\textsf{PDPEX(va)} = \textsf{pdp\_entry} \land \textsf{table\_root(pml4\_entry}_{\textsf{pfn}})  = \textsf{pdp}}_{\rtv}$
$\specline{\textsf{P} \ast \mathcal{I}\texttt{ASpace}_{\textsf{id}}(\theta,\Xi\setminus\{\textsf{plm4\_entry},\textsf{pdp\_entry}\},m)  }_{\rtv}$
$\specline{\ghostmaptoken{\textsf{id}}{(\mathsf{plm4\_entry})}{\textsf{4}} \ast \ghostmaptoken{\delta{}s}{\rtv}{\delta}  }_{\rtv}$
$\specline{\forall_{i\in\textsf{0..511}} \; \textsf{table\_root(plm4\_entry}_{\textsf{pfn}}) \textsf{ + i * 8} \mapsto_{\textsf{id}} \textsf{3} }_{\rtv}$
$\specline{ \textsf{plm4\_entry+KERNBASE} \mapsto_{\textsf{vpte,qfrac}} \textsf{l4e\_val} \ast \ulcorner  \textsf{qfrac} = 1 \leftrightarrow \; \lnot(\textsf{entry\_present entry\_val})\urcorner}_{\rtv}$
$\specline{ \textsf{pdp\_entry+KERNBASE} \mapsto_{\textsf{vpte,qfrac}} \textsf{l3e\_val} \ast \ghostmaptoken{\textsf{id}}{(\mathsf{pdp\_entry})}{\textsf{3}}}_{\rtv}$
$\specline{\begin{array}{l} \textsf{entry\_present(l3e\_val)} -* \\  \;\;\;\;\;\;\; \forall_{i\in\textsf{0..511}} \; \textsf{table\_root(pdp\_entry}_{\textsf{pfn}}) \textsf{ + i * 8} \mapsto_{\textsf{id}} \textsf{2}    \end{array}}_{\rtv} $
$\specline{\ulcorner  \textsf{qfrac} = 1 \leftrightarrow \; \lnot(\textsf{entry\_present l3e\_val})\urcorner}_{\rtv}$

@@

 $\specline{\textsf{P} \ast \textsf{plm4} \mapsto_{\textsf{id}} \textsf{\_} \ast \mathcal{I}\texttt{ASpace}_{\textsf{id}}(\theta,\Xi,m) \ast \ghostmaptoken{\delta{}s}{\rtv}{\delta}}_{\rtv}$      

@@

@@

$\specline{ \left( \begin{array}{l} \textsf{pdp}+\textsf{PDPEX(va)} = \textsf{pdp\_entry} \land \textsf{table\_root(pml4\_entry}_{\textsf{pfn}})  = \textsf{pdp} \\ \textsf{pd}+\textsf{PDEX(va)} = \textsf{pd\_entry} \land \textsf{table\_root(pml3\_entry}_{\textsf{pfn}})  = \textsf{pd} \\ \textsf{pt}+\textsf{PDPEX(va)} = \textsf{pt\_entry} \land \textsf{table\_root(pml2\_entry}_{\textsf{pfn}})  = \textsf{pt} \\  \textsf{P} \ast \mathcal{I}\texttt{ASpace}_{\textsf{id}}(\theta,\Xi\setminus\{\textsf{plm4\_entry},\textsf{pdp\_entry},\textsf{pd\_entry},\textsf{pt\_entry}\},m)  \\ \ghostmaptoken{\delta{}s}{\rtv}{\delta} \\
\ghostmaptoken{\textsf{id}}{(\mathsf{plm4\_entry})}{\textsf{4}}\ast \ghostmaptoken{\textsf{id}}{(\mathsf{plm3\_entry})}{\textsf{3}} \ast \ghostmaptoken{\textsf{id}}{(\mathsf{plm2\_entry})}{\textsf{2}}  \\ \forall_{i\in\textsf{0..511}} \; \textsf{table\_root(plm4\_entry}_{\textsf{pfn}}) \textsf{ + i * 8} \mapsto_{\textsf{id}} \textsf{3}  \\ \forall_{i\in\textsf{0..511}} \; \textsf{table\_root(pdp\_entry}_{\textsf{pfn}}) \textsf{ + i * 8} \mapsto_{\textsf{id}} \textsf{2}  \\ \forall_{i\in\textsf{0..511}} \; \textsf{table\_root(pd\_entry}_{\textsf{pfn}}) \textsf{ + i * 8} \mapsto_{\textsf{id}} \textsf{1}  \\  \textsf{plm4\_entry+KERNBASE} \mapsto_{\textsf{vpte,qfrac}} \textsf{l4e\_val} \ast \ulcorner  \textsf{qfrac} = 1 \leftrightarrow \; \lnot(\textsf{entry\_present l4e\_val})\urcorner \\  \textsf{pdp\_entry+KERNBASE} \mapsto_{\textsf{vpte,qfrac}} \textsf{l3e\_val} \ast \ulcorner  \textsf{qfrac} = 1 \leftrightarrow \; \lnot(\textsf{entry\_present l3e\_val})\urcorner \\  \textsf{pd\_entry+KERNBASE} \mapsto_{\textsf{vpte,qfrac}} \textsf{l2e\_val} \ast \ulcorner  \textsf{qfrac} = 1 \leftrightarrow \; \lnot(\textsf{entry\_present l2e\_val})\urcorner \\   \textsf{pt\_entry+KERNBASE} \mapsto_{\textsf{vpte,qfrac}} \textsf{l1e\_val} \ast \ulcorner  \textsf{qfrac} = 1 \leftrightarrow \; \lnot(\textsf{entry\_present l1e\_val})\urcorner    \end{array} \right)  =\textsf{R}_{\textsf{walk\_acc}}}$

@@

$\specline{\textsf{pt\_entry}_{\textsf{pfn}} \mapsto_{p} \textsf{addr\_to\_pfn}(\textsf{pa})}_{\rtv}$

@@

  \caption{Specification and proof of code for mapping a new page with $\textsf{R}_{\textsf{walk\_acc}}$ in Figure \ref{walkpgdir} expanded.}
